---
title: "Two Function"
author: "20043"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Two Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# shrinkage

This function can get the R-square's k-fold cross validation to evaluate 
the generalization ability of regression model. We can get the orignal R-square and
the k-fold cross-validated R-square.The less the R-square is reduced, the more accurate the prediction is.

```{r}
library(bootstrap)
shrinkage <- function(fit, k){
  
  
  theta.fit <- function(x,y){lsfit(x,y)}
  theta.predict <- function(fit, x){cbind(1,x)%*%fit$coef}
  
  x <- fit$model[,2:ncol(fit$model)]
  y <- fit$model[,1]
  
  results <- crossval(x, y, theta.fit, theta.predict, ngroup=k)
  r2 <- cor(y, fit$fitted.values)^2
  r2cv <- cor(y, results$cv.fit)^2
  cat("Original R-square =", r2, "\n")
  cat(k, "Fold Cross-Validated R-square =", r2cv, "\n")
  cat("Change =", r2-r2cv, "\n")
}

fit <- lm(mpg ~ hp + drat+ wt+ qsec, data=mtcars)
k=10
shrinkage(fit,k)
```


# relweights

This function compute the relative weights of each predictor variable of the regression model.
We can see the degree to which each predictor variable explains the model variance.
And we can know that which variable is important.

```{r}
relweights <- function(fit){
  R <- cor(fit$model)
  nvar <- ncol(R)
  rxx <- R[2:nvar, 2:nvar]
  rxy <- R[2:nvar, 1]
  svd <- eigen(rxx)
  evec <- svd$vectors
  ev <- svd$values
  delta <- diag(sqrt(ev))
  lambda <- evec %*% delta %*% t(evec)
  lambdasq <- lambda^2
  beta <- solve(lambda) %*% rxy
  rsquare <- colSums(beta^2)
  rawwgt <- lambdasq %*% beta^2
  import <- (rawwgt / rsquare)*100
  lbls <- names(fit$model[2:nvar])
  rownames(import) <- lbls
  colnames(import) <- "Weights"
  barplot(t(import),names.arg=lbls, ylab="% of R-square", xlab="Predictor Variables", 
          main="Relative Importance of Predictor Variables", sub=paste("r-square=", round(rsquare, digits=3)))
  return(import)
}

fit <- lm(mpg ~ hp + drat+ wt + qsec, data=mtcars)
relweights(fit)
```

